The pollination trade-off

### 2019-03-14 paper/supp-info.Rmd
Make correlation figure in supp info a bit taller

```{r fig-correlation, fig.height = 4.5, fig.cap = "Corelation between the explanatory variables included in the statistical models.", eval=T}
drake::readd(fig_correlation)
```

>>>>

```{r fig-correlation, fig.height = 5, fig.cap = "Corelation between the explanatory variables included in the statistical models.", eval=T}
drake::readd(fig_correlation)
```
